---
title: "WebScraper"
author: "Madeline Hoshko"
date: "October 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
pkgs = c("rvest", "magrittr", "httr", "stringr", "dplyr", "tidyr")
  for (pkg in pkgs){
    if (!require(pkg, character.only = T)){
      install.packages(pkg)
      library(pkg)
    }
  }
```

My read_class_schedule function takes in a given url to then read the html to scrape for information on the class subject, class number, section number, class title, instructor, and enrollment total. It then returns a tibble of the attributes. 

```{r}
read_class_schedule <- function(url){
  webpage = read_html(url)
  subject <- webpage %>%
    html_nodes("td.subj") %>%
    html_text()
  class_number <- webpage %>%
    html_nodes("td.cat_num") %>%
    html_text()
  section_number <- webpage %>%
    html_nodes("td.sect") %>%
    html_text()
  class_title <- webpage %>%
    html_nodes("td.title") %>%
    html_text()
  instructor <- webpage %>%
    html_nodes("td.Instructor") %>%
    html_text()
  enrollment_total <- webpage %>%
    html_nodes("td.enrtot") %>%
    html_text()

  tib <- tibble(subject=subject, class_number=class_number, section_number=section_number, class_title=class_title, instructor=instructor, enrollment_total=enrollment_total)
  return(tib)
}

```


I now call read_class_schedule for the Spring 2019 Math and Computer Science catalogs as well as the Spring 2020 Math and Computer Science catalogs. With the result, I use rbind to join together all four tibbles into one. Since they have the same attributes I am able to use rbind to append the tibbles to each other vertically. 
```{r}
(CS2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml"))
(CS2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml"))
(MATH2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/MATH.shtml"))
(MATH2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/MATH.shtml"))
(composite <- rbind(CS2019, CS2020, MATH2019, MATH2020))

```

